%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[a4paper, 12pt]{article}
\usepackage{enumitem} % for leftmargin of itemize
\usepackage{sectsty} % for section styling like header font size

% LAYOUT %
% Font
%% Set \header command
\makeatletter
\newcommand\header{\@setfontsize\Huge{14}{14}} % for my name
\makeatother

\sectionfont{\fontsize{12}{12}\selectfont}

% Margins
\usepackage[margin=1in]{geometry} % for page margin

% Indentation
\setlength\parindent{.5in}

% Page Numbering
\pagenumbering{gobble}

% Table
\setlength{\arrayrulewidth}{0mm}
\setlength{\tabcolsep}{1pt}


% DOCUMENT %
\begin{document}

\noindent
\textbf{\header Michael L. Otte}
\vspace{-3mm}

\noindent
\line(1,0){452}\\[2mm]
\begin{tabular}{ |p{2.9in}|p{3.75in}| }
{\sl Cell:} (831) 704-6563 & {\sl LinkedIn:} www.linkedin.com/in/michaelotte13 \\[0mm]
{\sl Email:} MichaelOtte1@gmail.com & {\sl GitHub:} www.github.com/motte \\[3mm]
\end{tabular}\\[-5mm]

\section*{SELECTED EXPERIENCES}
\vspace{-3mm}

{\bf Freenome}{, South San Francisco, CA}\hfill {\bf September 2015-Current \\}
{\sl CTO, VP of Product, Software Engineer - freenome.com} \newline
\indent I created several big data pipelines, alone and in a small team, that process raw genomic data (raw read data), conduct automated or semi-automated feature selection, and input into various statistical learning methods (e.g. various perceptrons, random forest, and more).  With the uniquely challenging "big" dataset, I had the opportunity to implement a number of feature selectors on the genomic datasets in various AMQP systems and format them into different types of matrices.  These pipelines improved efficiency of processing by 10-100X.

\indent I also developed a lung cancer risk prediction application and a web-based genome browser (a visualization to analyze one or more genomic samples), which is often used for manual pattern recognition, analysis, and inter-sample comparison from vcf format files (essentially analytical/processed files of genetic variants).  For about a year, I worked with engineers at Google, Microsoft Azure, and AWS to implement feature suggestions on their platform and improve their big data and genomics/bioinformatics offerings (e.g. Google cloud functions, azure IAMs, Google genomics, etc.). \\[-6mm]
\begin{itemize}[leftmargin=5mm] 
\itemsep -2pt
	\item Helped grow the company from 4 to ~30 people and raise over \$70 million
	\item Created, lead, and developed 3+ critical projects (using Python, React, HTML/CSS/ES6)
	\item Worked with ML experts and mathematicians to implement statistical models
\end{itemize}
\vspace{0.5mm}
\noindent
{\bf Acorn}{, New York, NY - \sl Exited/Closed}\hfill {\bf May 2014-May 2015 \\}
{\sl COO, Lead Engineer, Co-Founder - www.facebook.com/acornapp/ (formerly acornapp.co)} \\
\indent Coded a novel, patented location-acquisition tech for mobile.  Setup a highly scalable distributed system.  Coded a RWD web application that was rated over 90\% by Google Page Speed and Yahoo YSlow by utilizing image compression to JS minimization.  This reduced overall latency and page load speeds by over 80\%.  Also, created a mobile-server client API and an OAuth 2.0 Protocol API to enable more powerful and modular computations for the mobile app.
%\begin{itemize}[leftmargin=5mm] 
%\itemsep -2pt
%	\item Helped develop two novel IPs in location acquisition tech
%	\item Full Stack Web and Mobile Development with backend API server
%\end{itemize}
                 
\section*{RECENT DEVELOPMENT EXPERIENCE}
\vspace{-3mm}
Python, Javascript (including React, Node.js, Angular.js, jQuery), HTML5+CSS3, PostgreSQL, MySQL, Nginx + gunicorn + uWsgi, shell scripting, PHP ($\sim$2010), Java ($\sim$2007)
                 
\section*{EDUCATION}
\vspace{-3mm}
{\bf Dartmouth College}, Hanover, NH - {\sl Socio-Cultural Anthropology} \hfill June 2013
                 
\section*{INTERESTS}
\vspace{-3mm}
I enjoy contributing to open source projects (e.g. Airflow), conducting biological and ethnographic research, rock climbing, surfing, singing, and volunteering.  I started coding in Hypercard when I was 10, and proceeds from my freelance work were donated to charities (e.g. UNICEF).  I used to be an EMT (an "ambulance driver") and was the personal assistant to a former U.S. surgeon general.


                
\end{document}